%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://github.com/kyrios-jawad/}{\Large Syed Jawad Alam}} & Email: \href{mailto:contact.syedjawad@gmail.com}{contact.syedjawad@gmail.com}\\
  \href{https://www.linkedin.com/in/syed-jawad-alam/}{Linkedin} & Mobile: \href{tel:+923102173426}{+92-310-217-3426} \\
\end{tabular*}

\section*{Objective}
Dedicated and results-driven Lead Software Developer with 3+ years of experience in building scalable software solutions, optimizing processes, and leading cross-functional teams. Passionate about leveraging technology to solve complex problems, improve development efficiency, and deliver high-quality solutions that meet client needs. Seeking to contribute my expertise in software development, team leadership, and process optimization to a forward-thinking organization that values innovation and continuous growth.


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {Software Engineer I}{Oct 2014 -- Sep 2016}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {Odes}{Karachi, Pakistan}
      {Lead Software Developer}{Nov 2023 -- Present}
      \resumeItemListStart
        \resumeItem{Team Leadership and Development}
          {Led a team of developers in creating scalable and high-performance software solutions. Fostered a collaborative and inclusive environment, mentoring junior developers and ensuring successful project outcomes.}
        \resumeItem{Technical Strategy and Problem Solving}
          {Drove the technical strategy and architecture for key projects. Resolved complex technical issues, optimizing code performance and ensuring timely delivery of solutions that met business requirements.}
        \resumeItem{Process Optimization and Integration}
          {Identified and implemented opportunities for continuous integration and process improvement, resulting in a 20\% reduction in development time and enhanced software quality.}
        \resumeItem{Cross-functional Collaboration and Client Engagement}
          {Collaborated with cross-functional teams, including designers, product managers, and clients, to deliver tailored solutions that exceeded client expectations and contributed to long-term relationships.}
      \resumeItemListEnd


    \resumeSubheading
      {Maksof}{Karachi, Pakistan}
      {Junior Software Developer}{Sep 2022 -- Oct 2023}
      \resumeItemListStart
        \resumeItem{Collaboration and Process Improvement}
          {Coordinated with a dynamic software engineering team to develop scalable solutions. Collaborated with engineers and interns, identifying opportunities for continuous integration and process improvements.}
        \resumeItem{Technical Issue Resolution}
          {Created scalable code for customer business solutions, identified bugs, and resolved critical technical issues with the team. Proactively addressed challenges, contributing to process efficiency.}
        \resumeItem{Cross-functional Collaboration}
          {Fostered collaboration with developers, designers, and clients, delivering high-quality solutions that met client expectations.}
        \resumeItem{Employee Management System Development}
          {Developed an Employee Management System with finance, attendance, and employee modules. Reduced attendance errors by 20\% and improved client satisfaction by 25\%.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Custom Image Transition Script}
      {Developed a Python script powered by FFmpeg to create dynamic transition animations from images, offering effects like fade, slide, zoom, and blur. Supports multiple image formats, outputs in resolutions up to 1080p 60-120 FPS, and includes batch processing and background music options.}
    \resumeSubItem{TissueVend Embedded System}
      {Designed and developed an IoT-enabled embedded system for vending machines dispensing scented and unscented tissues, featuring secure user credential management, real-time monitoring, seamless online/offline operation, and smart inventory analytics.}
    \resumeSubItem{Custom Ubuntu-based Linux Distro}
      {Developed a lightweight, developer-friendly Linux distribution by customizing Ubuntu — removing unnecessary packages, optimizing system performance, and packaging it into a standalone installable ISO}
    \resumeSubItem{Linux Setup Book}
      {E-Book that gives step-by-step instructions on setting up developer environment on Linux.}
    \resumeSubItem{Express Api Boiler plate}
      {Express Api Boiler plate is a open source contribution for kickstart your clean architecture node.js project}
  \resumeSubHeadingListEnd

%
%--------SKILLS------------
\section{Skills}
 \resumeSubHeadingListStart
   \item{\textbf{Languages}{: JavaScript, TypeScript, Python, PHP, SQL, Postgres, MongoDB}}
   \item{\textbf{Technologies}{: React, NextJs, Angular, NodeJs, Laravel, Docker, Agile, AWS, Google Cloud API, Firebase, Supabase, GraphQL, Linux, Ngnix}}
 \resumeSubHeadingListEnd



%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Sindh Madressatul Islam University (SMIU)}{Karachi, Pakistan}
    {Bachelor of Science in Computer Science;}{Sep 2023 -- Sep 2024}
  \resumeSubheading
    {Aptech Learning}{Karachi, Pakistan}
    {Advance Diploma in Software Engineering; GPA: 3.5 (7.75/10.0)}{Aug 2020 -- Aug 2023}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
